Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
added graph and some fixes to section 4

Concurrent calls to $\offerfork$ must be protected by a mutex
to avoid racing on the
available workgroups. The same conflict over available workgroups can
occur at a new kernel launch between the scheduler and a workgroup
calling $\offerfork$.

The scheduler context provides an \emph{assignment mutes} to protect concurrent calls to
$\offerfork$ and $\offerkill$.  On calling $\offerkill$, a workgroup is only permitted to exit if the scheduler workgroup currently holds the assignment mutex; that is, the scheduler is trying to obtain work
groups to send to a task.  Conversely, on calling $\offerfork$ a workgroup can only spawn new workgroups if the scheduler workgroup does not hold the assignment mutex.  Thus the assignment mutex, only ever acquired by the scheduling workgroup, \emph{indirectly} provides mutual exclusion between a pairs of workgroups executing $\offerkill$ and $\offerfork$ concurrently. \ADComment{Please check previous -- I think I've got the coolness!}

Concurrent calls to $\offerkill$ are acceptable because only the
workgroup with the highest id may exit, automatically ensuring mutual
exclusion for exit-related modifications.

@@

In \mysec\ref{sec:semantics}, we defined the semantics of a resizing barrier in terms
of a series of calls to $\globalbarrier$, $\offerfork$ and $\offerkill$.
 It is possible, however to implement the resizing with
only one call to a global barrier with $\offerfork$ and $\offerkill$
baked into the implementation. \TSComment{note here that these
  implementations require no cfork or ckill outside of the barrier} \ADComment{Ignore until camera-ready?}

We consider barriers that use the master/slave model
(e.g.\ \cite{XF10}): one workgroup (the master) collects signals
from the other workgroups (the slaves) indicating that they have
arrived at the barrier and are waiting for a reply indicating that
they may leave the barrier. Once the master has recieved a signal from
all the slaves, it replies with a signal saying that the slaves may
leave. \TSComment{Need to discuss new active workgroup number that
is stable across iterations} \ADComment{Again, ignore until camera-ready?}

@@

>>>>

Concurrent calls to $\offerfork$ must be protected by a mutex to avoid
racing on the available workgroups. The same conflict over available
workgroups can occur at a new kernel launch between the scheduler and
a workgroup calling $\offerfork$. Thus, these activities are protected
by a mutex, called the \emph{assignment mutex} provided in the scheduler
context.

The assignment mutex additionally protects concurrent calls to
$\offerfork$ and $\offerkill$.  On calling $\offerkill$, a workgroup
is only permitted to exit if the scheduler workgroup currently holds
the assignment mutex; that is, the scheduler is trying to obtain work
groups to send to a task.  Conversely, on calling $\offerfork$ a
workgroup can only spawn new workgroups if the scheduler workgroup
does not hold the assignment mutex.  Thus the assignment mutex, only
ever acquired by the scheduling workgroup, \emph{indirectly} provides
mutual exclusion between a pairs of workgroups executing $\offerkill$
and $\offerfork$ concurrently.

Concurrent calls to $\offerkill$ are acceptable because only the
workgroup with the highest id may exit, automatically ensuring mutual
exclusion for exit-related state changes.

@@

In \mysec\ref{sec:semantics}, we defined the semantics of a resizing barrier in terms
of a series of calls to $\globalbarrier$, $\offerfork$ and $\offerkill$.
 It is possible, however to implement the resizing with
only one call to a global barrier with $\offerfork$ and $\offerkill$
baked into the implementation.

We consider barriers that use the master/slave model
(e.g.\ \cite{XF10}): one workgroup (the master) collects signals
from the other workgroups (the slaves) indicating that they have
arrived at the barrier and are waiting for a reply indicating that
they may leave the barrier. Once the master has recieved a signal from
all the slaves, it replies with a signal saying that the slaves may
leave.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{heavy.pdf} 
\caption{Blah}\label{fig:blah}
\end{figure}
